Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-10-04 DryDep.tex
Small change in tense.

Based on the global atmospheric composition reanalysis performed in the ECWMF project Monitoring Atmospheric Composition and Climate (MACC) \citep{MACC-II} and a more realistic process-based oceanic deposition scheme, \citet{ACP:Luhar2018} found that the ozone dry deposition to oceans amounts to $98.4 \pm 30.0\,\unit{Tg\,a^{-1}}$. In particular, \citet{ACP:Luhar2018} find that the average surface resistance of ozone over ocean ($r_c=2200\,\unit{sm^{-1}}$) is highly overestimated in most models.

>>>>

Based on the global atmospheric composition reanalysis performed in the ECWMF project Monitoring Atmospheric Composition and Climate (MACC) \citep{MACC-II} and a more realistic process-based oceanic deposition scheme, \citet{ACP:Luhar2018} found that the ozone dry deposition to oceans amounts to $98.4 \pm 30.0\,\unit{Tg\,a^{-1}}$. In particular, \citet{ACP:Luhar2018} found that the average surface resistance of ozone over ocean ($r_c=2200\,\unit{sm^{-1}}$) is highly overestimated in most models.
